Social Conditions of Fear

### 2023-11-28 scripts/manuscript.qmd
figure 1

library(tidyverse)
library(dplyr)
library(tidyr)
library(here)
library(rio)
library(janitor)
library(knitr)
library(kableExtra)
library(mice)
library(forcats)
```

@@

```{r}
#| label: mice imputation
# DO NOT RUN 
complete5 <- mice(na_data, 
                 m = 50, 
                 seed = 25)

@@

@@

```{r}
```

>>>>

library(tidyverse)
library(dplyr)
library(tidyr)
library(here)
library(rio)
library(janitor)
library(knitr)
library(kableExtra)
library(mice)
library(forcats)
library(ggplot2)
```

@@

```{r}
#| label: mice imputation
#| eval: false
complete5 <- mice(na_data, 
                 m = 50, 
                 seed = 25)

@@

  mutate(fear = factor(case_when(fear == "NO" ~ "no",
                                 fear == "YES" ~ "yes"))) %>% 

@@

```{r}
#| label: creating a smaller subset from data

gss_subset <- tidydata %>% 
  select(age, sexnow1, racecombo, uscitzn, degree, attend, raclive, happy, health, 
         partnrs5, fear) 
```

```{r}
#| label: pivot longer and pivot wider to get proportion of yes and no by race and display on a table
#| eval: false

temp <- gss_subset %>% 
  pivot_longer(
    cols = fear,
    names_to = "fear",
    values_to = "answer") %>% 
  select(racecombo, answer) %>% 
  mutate(fear = as.numeric(case_when(answer == "no" ~ "0",
                                 answer == "yes" ~ "1"))) %>% 
  select(racecombo, fear)

%>% 
  pivot_wider(
    names_from = racecombo,
    values_from = fear
  )

%>% 
  group_by(racecombo)

%>% 
  summarize(proportion = fear /sum(fear == "yes", na.rm = TRUE)) %>% 
  kable(caption = "Proportion Social Fear by Race",
        col.names = c("Race", "Proportion"),
        digits = 1,
        booktabs = TRUE)

```{r}
#| label: fig-fear_race
#| fig-cap: Bar graph showing the proportion or respondants, by race, that feared walking alone at night.

tidydata %>% 
  filter(!is.na(racecombo)) %>% 
  filter(racecombo != "Other") %>% 
  ggplot(aes(x = racecombo, y = after_stat(prop), group = fear, 
             fill = fear)) +
  geom_bar(position = "dodge") + 
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Social Fear by Race",
       caption = "Question: Is there any area right around here--that is, within a mile--where you would be afraid to walk alone at night?",
       x = "Race",
       y = NULL,
       fill = "Fear"
       ) +
  theme_bw()
